---
title: "NewsFormatStats"
author: "Lisa Matthias"
date: "25 9 2023"
output: 
  html_document: 
    keep_md: true
    toc: yes
    toc_float: yes
    theme: readable
    code_folding: hide
---

```{r setup, echo=FALSE}

#set up knit r global
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  fig.width = 6,
  fig.asp = 0.618,
  out.width = "70%",
  fig.align = "center",
  dpi = 300)
```

```{r packages, echo=FALSE}
library(datawizard)
#library(ggstatsplot)
library(gt)
library(janitor)
library(tidyverse)
```

```{r main-data, echo=FALSE}
# Read the "NewsMentionsSample" sheet from the local copy. Call this "mntn_raw"
mntn_raw <- read.csv("data/NewsMentionSample.csv")

```

```{r variable-transformation, echo=FALSE}
# Set factor levels and labels
IssueAreaLevels <- c(
  "Abortion", "EconomicActivity",
  "FirstAmendment",
  "SexDiscrimination"
)

CaseStageLevels <- c(
  "Cert", "PostCert", "Argument",
  "PostArgument", "Decision",
  "PostDecision"
)

ChannelTypeLevels <- c("NetworkNews", "CableNews")

TimePeriodLevels <- c("2000_2018", "1990_1999")

# Mutate columns in mntn_raw
mntn_raw$IssueArea <- factor(mntn_raw$IssueArea,
  levels = IssueAreaLevels
)


mntn_raw$CaseStage <- factor(mntn_raw$CaseStage,
  levels = CaseStageLevels
)

mntn_raw$ChannelType <- factor(mntn_raw$ChannelType,
  levels = c("NetworkNews", "CableNews")
)

mntn_raw$NewsProgram <- factor(mntn_raw$NewsProgram, levels = c("Hardball", "SpecialReport", "WorldNewsTonight"))

mntn_raw$TimePeriod <- factor(mntn_raw$TimePeriod,
  levels = TimePeriodLevels
)

mntn_raw$CaseStageCondensed <- fct_collapse(mntn_raw$CaseStage,
  "PreDecision" = c(
    "Cert", "PostCert",
    "Argument", "PostArgument"),
  "Decision" = "Decision",
  "PostDecision" = "PostDecision"
)

mntn_raw$CaseStageCondensed <- factor(mntn_raw$CaseStageCondensed, levels = c("PreDecision", "Decision", "PostDecision"))

mntn_raw$MentionContext <- factor(mntn_raw$MentionContext,
                                levels = c("1", "2", "3"))

mntn_raw$AnchorOnly <- as.numeric(as.character(mntn_raw$AnchorOnly))
mntn_raw$Correspondent <- as.numeric(as.character(mntn_raw$Correspondent))
mntn_raw$Debate <- as.numeric(as.character(mntn_raw$Debate))
mntn_raw$NewsInterview <- as.numeric(as.character(mntn_raw$NewsInterview))

mntn_raw$WordCountRAND <- as.numeric(mntn_raw$WordCountRAND)

```

```{r data-subsets, echo=FALSE}
#Create new column with collapsed channel types
df_channel_split <- mntn_raw %>%
  mutate(ChannelTypeSplit = case_when(ChannelType == "CableNews" &  TimePeriod == "2000_2018" ~ "CableNews", ChannelType == "NetworkNews" &  TimePeriod == "2000_2018" ~ "NetworkNewsPost2000", ChannelType == "NetworkNews" &  TimePeriod == "1990_1999" ~ "NetworkNewsPre2000"))

#Convert new column to factor
ChannelTypeSplitLevels <- c("NetworkNewsPre2000","NetworkNewsPost2000","CableNews")

df_channel_split$ChannelTypeSplit <- factor(df_channel_split$ChannelTypeSplit, levels = ChannelTypeSplitLevels, labels = ChannelTypeSplitLevels)

#Robustness set with identical news mentions included only once
# Create a new dataframe that only includes entries with "MultiMentionMentionType" == "identical"
df_channel_split_identical <- df_channel_split[df_channel_split$MultiMentionType == "Identical",]

# Use the unique function to only keep the first instance of each "TranscriptID" for identicals
df_channel_split_identical <- df_channel_split_identical[!duplicated(df_channel_split_identical$TranscriptID),]

# Create a new dataframe that only includes entries with "MultiMentionMentionType" != "identical"
df_channel_split_non_identical <- df_channel_split[df_channel_split$MultiMentionType != "Identical",]

# Concatenate the filtered dataframes
df_channel_split_robust <- rbind(df_channel_split_non_identical, df_channel_split_identical)
```

```{r chisq-news-segment-format-functions, echo=FALSE}
#Function for chisq pre-2000 & post-2000 network news ~ segment formats
function_chisq_SegmentFormat_time <- function(df, news_var, SegmentFormat){
  news_var <- sym(news_var)
  SegmentFormat <- sym(SegmentFormat)
  
  x <- df %>%
  filter(ChannelTypeSplit != "CableNews") %>%
  mutate_if(is.numeric,as.factor) %>%
  tabyl(!!news_var , !! SegmentFormat, show_missing_levels = FALSE) %>%
  chisq.test(correct = FALSE)
  
  return(x)
}

function_chisq_SegmentFormat_channel <- function(df, news_var, SegmentFormat){
  news_var <- sym(news_var)
  SegmentFormat <- sym(SegmentFormat)

  x <- df %>%
  filter(ChannelTypeSplit != "NetworkNewsPre2000") %>%
  mutate_if(is.numeric,as.factor) %>%
  tabyl(!!news_var, !!SegmentFormat, show_missing_levels = FALSE) %>%
  chisq.test(correct = FALSE)
  
  return(x)
}

#Function for chisq cable programs ~ segment formats
function_chisq_SegmentFormat_cable <- function(df, news_var, SegmentFormat){
  news_var <- sym(news_var)
  SegmentFormat <- sym(SegmentFormat)
  
  x <- df %>%
  filter(ChannelTypeSplit == "CableNews") %>%
  mutate_if(is.numeric,as.factor) %>%
  tabyl(!!news_var, !!SegmentFormat, show_missing_levels = FALSE) %>%
  chisq.test(correct = FALSE)
  
  return(x)
}

#Function to print chisq results, observed values, expected values, and standardized residuals
consolidate_chisq_results <- function(chisq_context_time, context_col) {
  
  observed <- chisq_context_time$observed
  expected <- chisq_context_time$expected
  stdres <- chisq_context_time$stdres
  
  # Dynamically get the name of the first column
  first_col_name <- colnames(observed)[1]
  
  if (context_col == "Present") {
    result_df <- data.frame(
      FirstColumn = observed[, 1],
      Observed_1 = observed[, 2],
      Observed_2 = observed[, 3],
      Expected_1 = expected[, 2],
      Expected_2 = expected[, 3],
      StdRes_1 = stdres[, 2],
      StdRes_2 = stdres[, 3]
    )
  } else {
    result_df <- data.frame(
      FirstColumn = observed[, 1],
      Observed_1 = observed[, 2],
      Observed_2 = observed[, 3],
      Observed_3 = observed[, 4],
      Expected_1 = expected[, 2],
      Expected_2 = expected[, 3],
      Expected_3 = expected[, 4],
      StdRes_1 = stdres[, 2],
      StdRes_2 = stdres[, 3],
      StdRes_3 = stdres[, 4]
    )
  }
  
  long_df <- result_df %>%
    pivot_longer(
      cols = starts_with("Observed") | starts_with("Expected") | starts_with("StdRes"),
      names_to = c(".value", context_col),
      names_pattern = "(Observed|Expected|StdRes)_(\\d+)"
    ) %>%
    select(FirstColumn, all_of(context_col), Observed, Expected, StdRes) %>%
    rename_at(vars(FirstColumn), ~first_col_name)  # Rename 'FirstColumn' back to its original name
  
 long_df <- long_df %>%
    mutate(
      !!context_col := case_when(
        context_col == "Present" ~ factor(!!sym(context_col), levels = c("1", "2"), labels = c("No", "Yes")),
        context_col == "MentionContext" ~ factor(!!sym(context_col), levels = c("1", "2", "3"), labels = c("Same", "Related", "Different")),
        context_col == "MntnLengthGroup" ~ factor(!!sym(context_col), levels = c("1", "2", "3"), labels = c("Short", "Medium", "Long")),
        TRUE ~ as.factor(!!sym(context_col))
      ),
      Expected = round(Expected, digits = 2),
      StdRes = round(StdRes, digits = 2)
    )
  
  return(long_df)
}

```

## Mention Context
This compares the news mentions based on the context they were mentioned in: Same (1), Related (2), Different (3)

### Network News Time Period
Compares network news mentions from the 1990-1999 and 2000-2018 terms.
```{r chisq-context-time, results='asis'}
#Create contingency table for Channel Types and Mention Contexts 
df_context_time_channel <- df_channel_split %>%
  xtabs(~ MentionContext + ChannelTypeSplit, data = .)

#Convert xtabs into matrix
df_context_time_channel <- as.data.frame.matrix(df_context_time_channel) %>%
#Transpose matrix
  t() %>%
#Convert into tibble, so that rownames become categorical variables (needed for tabyl) 
  as_tibble(rownames = "ChannelTypeSplit") %>%
#Convert to tabyl to use chisq
  as_tabyl(df_context_time_channel, axes = 2) %>%
#Convert ChannelTypeSplit to a factor
  mutate(ChannelTypeSplit = factor(ChannelTypeSplit))

#chissq test on filtered contingency tables
chisq_context_time <- df_context_time_channel %>%
  filter(ChannelTypeSplit != "CableNews") %>%
  chisq.test(correct = FALSE)

chisq_context_time
```


```{r chisq-context-time-extra, include=FALSE}

chisq_context_time_results <- consolidate_chisq_results(chisq_context_time, context_col = "MentionContext") %>%
  group_by(MentionContext)%>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()) %>%
  tab_footnote(
  footnote = "A = Pre-2000 Network News; B = Post-2000 Network News"
)

chisq_context_time_results
```

#### Robustness Check
```{r chisq-context-time-robust, results = 'asis'}
#Create contingency table for Channel Types and Mention Contexts 
df_context_time_channel_robust <- df_channel_split_robust %>%
  xtabs(~ MentionContext + ChannelTypeSplit, data = .)


df_context_time_channel_robust <- as.data.frame.matrix(df_context_time_channel_robust) %>%
  t() %>%
#Convert into tibble, so that rownames become categorical variables (needed for tabyl) 
  as_tibble(rownames = "ChannelTypeSplit") %>%
  as_tabyl(df_context_time_channel, axes = 2) %>%
  mutate(ChannelTypeSplit = factor(ChannelTypeSplit))

#chissq
chisq_context_time_robust <- df_context_time_channel_robust %>%
  filter(ChannelTypeSplit != "CableNews") %>%
  chisq.test(correct = FALSE)

chisq_context_time_robust
    
```


### Channel Type
Compares network and cable news mentions from the 2000-2018 terms.
```{r chisq-context-channel, results='asis'}

chisq_context_channel <- df_context_time_channel %>%
  filter(ChannelTypeSplit != "NetworkNewsPre2000") %>%
  chisq.test(correct = FALSE)

chisq_context_channel
```


```{r chisq-context-channel-extra}

chisq_context_channel_results <- consolidate_chisq_results(chisq_context_channel, context_col = "MentionContext") %>%
  group_by(MentionContext)%>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()) %>%
  tab_footnote(
  footnote = "A = Post-2000 Network News; B = Cable News"
)

chisq_context_channel_results
```

#### Robustness Check
```{r chisq-context-channel-robust, results = 'asis'}

chisq_context_channel_robust <- df_context_time_channel_robust %>%
  filter(ChannelTypeSplit != "NetworkNewsPre2000") %>%
  chisq.test(correct = FALSE)

chisq_context_channel_robust
```


### Cable News Program
Compares Hardball (MSNBC) and Special Report (Fox News) news mentions from 2000-2018 terms.

```{r chisq-context-cable, results='asis'}
#Create contingency table for Channel Types and Mention Contexts 
df_context_cable <- df_channel_split %>%
  xtabs(~ MentionContext + NewsProgram, data = .)

#Convert xtabs into df, and transpose df so that News Programs are the rows and mention contexts are the columns
df_context_cable <- as.data.frame.matrix(df_context_cable) %>%
  t() %>%
  as_tibble(rownames = "NewsProgram") %>%
  mutate(NewsProgram = factor(NewsProgram))

#df as tabyl so chisq.test works
df_context_cable <- as_tabyl(df_context_cable, axes = 2)

#chissq test on filtered contingency tables
chisq_context_cable <- df_context_cable %>%
  filter(NewsProgram != "WorldNewsTonight") %>%
  chisq.test(correct = FALSE)

chisq_context_cable
```

```{r chisq-context-cable-extra}

chisq_context_cable_results <- consolidate_chisq_results(chisq_context_cable, context_col = "MentionContext") %>%
  group_by(MentionContext)%>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()) %>%
  tab_footnote(
  footnote = "A = Hardball; B = Special Report"
)

chisq_context_cable_results

```

#### Robustness Check
```{r chisq-context-cable-robust, results = 'asis'}
#Create contingency table for Channel Types and Mention Contexts 
df_context_cable_robust <- df_channel_split_robust %>%
  xtabs(~ MentionContext + NewsProgram, data = .)

#Convert xtabs into df, and transpose df so that News Programs are the rows and mention contexts are the columns
df_context_cable_robust <- as.data.frame.matrix(df_context_cable_robust) %>%
  t() %>%
  as_tibble(rownames = "NewsProgram") %>%
  mutate(NewsProgram = factor(NewsProgram))

#df as tabyl so chisq.test works
df_context_cable_robust <- as_tabyl(df_context_cable_robust, axes = 2)

#chissq test on filtered contingency tables
chisq_context_cable_robust <- df_context_cable_robust %>%
  filter(NewsProgram != "WorldNewsTonight") %>%
  chisq.test(correct = FALSE)

chisq_context_cable_robust

```

## Segment Format

This compares the number of news mentions that include one of four segment formats: anchor-only, correspondent, debate, and news interview. News mentions were coded for the presence and absence of each format.

### Network News Time Period
Compares network news mentions from the 1990-1999 and 2000-2018 terms.

**Anchor-Only**
```{r chisq-format-anchor-time, results='asis'}
#Chi-Squared for pre-2000 and post-2000 network news ~ news segment format
##Anchor Segments
chisq_anchor_time <- function_chisq_SegmentFormat_time(df_channel_split, news_var = "ChannelTypeSplit", SegmentFormat = "AnchorOnly")

chisq_anchor_time
```

```{r chisq-format-anchor-time-extra, include=FALSE}
chisq_anchor_time_results <- consolidate_chisq_results(chisq_anchor_time, context_col = "Present") %>%
  group_by(Present) %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()) 

chisq_anchor_time_results

```

**Correspondent**
```{r chisq-format-correspondent-time, results='asis'}
##Correspondent Segments
chisq_correspondent_time <- function_chisq_SegmentFormat_time(df_channel_split, news_var = "ChannelTypeSplit", SegmentFormat = "Correspondent")

chisq_correspondent_time

```


```{r chisq-format-correspondent-time-extra, include=FALSE}
chisq_correspondent_time_results <- consolidate_chisq_results(chisq_correspondent_time, context_col = "Present") %>%
  group_by(Present) %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()) 

chisq_correspondent_time_results

```

**News Interview**
```{r chisq-format-interview-time, results='asis'}
##News Interview Segments
chisq_interview_time <- function_chisq_SegmentFormat_time(df_channel_split, news_var = "ChannelTypeSplit", SegmentFormat = "NewsInterview")

chisq_interview_time
```

```{r chisq-format-interview-time-extra, include=FALSE}

chisq_interview_time_results <- consolidate_chisq_results(chisq_interview_time, context_col = "Present") %>%
  group_by(Present) %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()) 

chisq_interview_time_results
```

#### Robustness Check

**Anchor-Only**
```{r chisq-format-anchor-time-robust, results = 'asis'}
#Chi-Squared for pre-2000 and post-2000 network news ~ news segment format
##Anchor Segments
chisq_anchor_time_robust <- function_chisq_SegmentFormat_time(df_channel_split_robust, news_var = "ChannelTypeSplit", SegmentFormat = "AnchorOnly")

chisq_anchor_time_robust
```

**Correspondent**
```{r chisq-format-correspondent-time-robust, results = 'asis'}
##Correspondent Segments
chisq_correspondent_time_robust <- function_chisq_SegmentFormat_time(df_channel_split_robust, news_var = "ChannelTypeSplit", SegmentFormat = "Correspondent")

chisq_correspondent_time_robust
```

**News Interview**
```{r chisq-format-interview-time-robust, include = FALSE, eval = FALSE}
##News Interview Segments
chisq_interview_time_robust <- function_chisq_SegmentFormat_time(df_channel_split_robust, news_var = "ChannelTypeSplit", SegmentFormat = "NewsInterview")

chisq_interview_time_robust
```

### Channel Type
Compares network and cable news mentions from the 2000-2018 terms.

**Anchor-Only**
```{r chisq-format-anchor-channel, results='asis'}
#Chi-Squared for post-2000 network news and cable news ~ news segment format
##Anchor Segments
chisq_anchor_channel <- function_chisq_SegmentFormat_channel(df_channel_split, news_var = "ChannelTypeSplit", SegmentFormat = "AnchorOnly")

chisq_anchor_channel

```

```{r chisq-format-anchor-channel-extra}
chisq_anchor_channel_results <- consolidate_chisq_results(chisq_anchor_channel, context_col = "Present") %>%
  group_by(Present) %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()) 

chisq_anchor_channel_results
```

**Correspondent**
```{r chisq-format-correspondent-channel, results='asis'}
##Correspondent Segments
chisq_correspondent_channel <- function_chisq_SegmentFormat_channel(df_channel_split, news_var = "ChannelTypeSplit", SegmentFormat = "Correspondent")

chisq_correspondent_channel
```

```{r chisq-format-correspondent-channel-extra}

chisq_correspondent_channel_results <- consolidate_chisq_results(chisq_correspondent_channel, context_col = "Present") %>%
  group_by(Present) %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()) 

chisq_correspondent_channel_results

```

**News Interview**
```{r chisq-format-interview-channel, results='asis'}
##News Interview Segments
chisq_interview_channel <- function_chisq_SegmentFormat_channel(df_channel_split, news_var = "ChannelTypeSplit", SegmentFormat = "NewsInterview")

chisq_interview_channel
```


```{r chisq-format-interview-channel-extra}

chisq_interview_channel_results <- consolidate_chisq_results(chisq_interview_channel, context_col = "Present") %>%
  group_by(Present) %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()) 

chisq_interview_channel_results

```

**Debate**
```{r chisq-format-debate-channel, results='asis'}
##Panel and Debate Segments
chisq_debate_channel <- function_chisq_SegmentFormat_channel(df_channel_split, news_var = "ChannelTypeSplit", SegmentFormat = "Debate")

chisq_debate_channel
```


```{r chisq-format-debate-channel-extra}
chisq_debate_channel_results <- consolidate_chisq_results(chisq_debate_channel, context_col = "Present") %>%
  group_by(Present) %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()) 

chisq_debate_channel_results
```


#### Robustness Check

**Anchor-Only**
```{r chisq-format-anchor-channel-robust, results = 'asis'}
#Chi-Squared for post-2000 network news and cable news ~ news segment format
##Anchor Segments
chisq_anchor_channel_robust <- function_chisq_SegmentFormat_channel(df_channel_split_robust, news_var = "ChannelTypeSplit", SegmentFormat = "AnchorOnly")

chisq_anchor_channel_robust
```

**Correspondent**
```{r chisq-format-correspondent-channel-robust, results = 'asis'}
##Correspondent Segments
chisq_correspondent_channel_robust <- function_chisq_SegmentFormat_channel(df_channel_split_robust, news_var = "ChannelTypeSplit", SegmentFormat = "Correspondent")

chisq_correspondent_channel_robust
```

**News Interview**
```{r chisq-format-interview-channel-robust, results = 'asis'}
##News Interview Segments
chisq_interview_channel_robust <- function_chisq_SegmentFormat_channel(df_channel_split_robust, news_var = "ChannelTypeSplit", SegmentFormat = "NewsInterview")

chisq_interview_channel_robust
```

**Debate**
```{r chisq-format-debate-channel-robust, results = 'asis'}
##Panel and Debate Segments
chisq_debate_channel_robust <- function_chisq_SegmentFormat_channel(df_channel_split_robust, news_var = "ChannelTypeSplit", SegmentFormat = "Debate")

chisq_debate_channel_robust
```

### Cable News Program
Compares Hardball (MSNBC) and Special Report (Fox News) mentions from the 2000-2018 terms.

**Anchor**
```{r chisq-anchor-cable, results='asis'}
#Chi-Squared for Hardball and Special Report ~ news segment format
##Anchor Segments
chisq_anchor_cable <- function_chisq_SegmentFormat_cable(df_channel_split, news_var = "NewsProgram", SegmentFormat = "AnchorOnly")

chisq_anchor_cable

```


```{r chisq-anchor-cable-extra}
chisq_anchor_cable_results <- consolidate_chisq_results(chisq_anchor_cable, context_col = "Present") %>%
  group_by(Present) %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()) 

chisq_anchor_cable_results

```

**Correspondent**
```{r chisq-correspondent-cable, results='asis'}
##Correspondent Segments
chisq_correspondent_cable <- function_chisq_SegmentFormat_cable(df_channel_split, news_var = "NewsProgram", SegmentFormat = "Correspondent")

chisq_correspondent_cable
```


```{r chisq-correspondent-cable-extra}
chisq_correspondent_cable_results <- consolidate_chisq_results(chisq_correspondent_cable, context_col = "Present") %>%
  group_by(Present) %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()) 

chisq_correspondent_cable_results
```

**News Interview**
```{r chisq-interview-cable, results='asis'}
##News Interview Segments
chisq_interview_cable <- function_chisq_SegmentFormat_cable(df_channel_split, news_var = "NewsProgram", SegmentFormat = "NewsInterview")

chisq_interview_cable
```

```{r chisq-interview-cable-extra}
chisq_interview_cable_results <- consolidate_chisq_results(chisq_interview_cable, context_col = "Present") %>%
  group_by(Present) %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()) 

chisq_interview_cable_results
```

**Debate**
```{r chisq-debate-cable, results='asis'}
##Panel and Debate Segments
chisq_debate_cable <- function_chisq_SegmentFormat_cable(df_channel_split, news_var = "NewsProgram", SegmentFormat = "Debate")

chisq_debate_cable
```


```{r chisq-debate-cable-extra}
chisq_debate_cable_results <- consolidate_chisq_results(chisq_debate_cable, context_col = "Present") %>%
  group_by(Present) %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()) 

chisq_debate_cable_results
```

#### Robustness Check
**Anchor-Only**
```{r chisq-format-anchor-cable-robust, results = 'asis'}
#Chi-Squared for post-2000 network news and cable news ~ news segment format
##Anchor Segments
chisq_anchor_cable_robust <- function_chisq_SegmentFormat_channel(df_channel_split_robust, news_var = "NewsProgram", SegmentFormat = "AnchorOnly")

chisq_anchor_cable_robust
```

**Correspondent**
```{r chisq-format-correspondent-cable-robust, results = 'asis'}
##Correspondent Segments
chisq_correspondent_cable_robust <- function_chisq_SegmentFormat_channel(df_channel_split_robust, news_var = "NewsProgram", SegmentFormat = "Correspondent")

chisq_correspondent_cable_robust
```

**News Interview**
```{r chisq-format-interview-cable-robust, results = 'asis'}
##News Interview Segments
chisq_interview_cable_robust <- function_chisq_SegmentFormat_channel(df_channel_split_robust, news_var = "NewsProgram", SegmentFormat = "NewsInterview")

chisq_interview_cable_robust
```

**Debate**
```{r chisq-format-debate-cable-robust, results = 'asis'}
##Panel and Debate Segments
chisq_debate_cable_robust <- function_chisq_SegmentFormat_channel(df_channel_split_robust, news_var = "NewsProgram", SegmentFormat = "Debate")

chisq_debate_cable_robust
```

## News Mention Length

This compares the share of news mentions based on their length: short (< 30 seconds), medium (> 30 seconds & < 2 minutes), long (> 2 minutes).

### Network News Time Period
Compares network news mentions from the 1990-1999 and 2000-2018 terms.
```{r chisq-mention-length-time, results='asis'}
#How long were Supreme Court case mentions on cable programs?
##Convert word count to seconds based on 135 words per 60 seconds/2.25 words per second (Edwards III & Howell, 2011, p. 258). Categorize mention length: short (shorter than 30 seconds), medium (31 seconds to 120 seconds), or long (longer than 120 seconds)

  mntn_length <- df_channel_split %>%
  mutate(MntnLengthSeconds = WordCountRAND/2.25) %>% 
  mutate(MntnLengthSeconds = round(MntnLengthSeconds, digits = 0)) %>%
  mutate(MntnLengthGroup = case_when(MntnLengthSeconds >= 120 ~ "Long",
                                     MntnLengthSeconds >= 30 ~ "Medium",
                                     MntnLengthSeconds < 30 ~ "Short")) %>%
  mutate(MntnLengthGroup = factor(.$MntnLengthGroup, 
                                  levels = c("Short", "Medium", "Long")))

##Contingency table ChannelTypeSplit ~ Mention Length
contingency_mntn_length_channel_time <-  mntn_length %>%
  tabyl(ChannelTypeSplit, MntnLengthGroup) 

chisq_mntn_length_time <- contingency_mntn_length_channel_time %>%
  filter(ChannelTypeSplit != "CableNews") %>%
  chisq.test(correct = FALSE)

chisq_mntn_length_time
```


```{r chisq-mention-length-time-extra, include=FALSE}
chisq_mntn_length_time_results <- consolidate_chisq_results(chisq_mntn_length_time, context_col = "MntnLengthGroup") %>%
  group_by(MntnLengthGroup) %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()) 

chisq_mntn_length_time_results
```

#### Robustness Check

```{r chisq-mention-length-time-robust, results = 'asis'}
#How long were Supreme Court case mentions on cable programs?
##Convert word count to seconds based on 135 words per 60 seconds/2.25 words per second (Edwards III & Howell, 2011, p. 258). Categorize mention length: short (shorter than 30 seconds), medium (31 seconds to 120 seconds), or long (longer than 120 seconds)
mntn_length_robust <- df_channel_split_robust %>%
  mutate(MntnLengthSeconds = WordCountRAND / 2.25) %>% 
  mutate(MntnLengthSeconds = round(MntnLengthSeconds, digits = 0)) %>%
  mutate(MntnLengthGroup = case_when(MntnLengthSeconds >= 120 ~ "Long",
                                     MntnLengthSeconds >= 30 ~ "Medium",
                                     MntnLengthSeconds < 30 ~ "Short")) %>%
  mutate(MntnLengthGroup = factor(.$MntnLengthGroup, 
                                  levels = c("Short", "Medium", "Long")))

##Contingency table ChannelTypeSplit ~ Mention Length
contingency_mntn_length_channel_time_robust <-  mntn_length_robust %>%
  tabyl(ChannelTypeSplit, MntnLengthGroup) 

chisq_mntn_length_time_robust <- contingency_mntn_length_channel_time_robust %>%
  filter(ChannelTypeSplit != "CableNews") %>%
  chisq.test(correct = FALSE)

chisq_mntn_length_time_robust
```

### Channel Type
Compares network and cable news mentions from the 2000-2018 terms.
```{r chisq-mention-length-channel, results='asis'}
chisq_mntn_length_channel <-  contingency_mntn_length_channel_time %>%
  filter(ChannelTypeSplit != "NetworkNewsPre2000") %>%
  chisq.test(correct = FALSE)

chisq_mntn_length_channel
```


```{r chisq-mention-length-channel-extra, include=FALSE}
chisq_mntn_length_channel_results <- consolidate_chisq_results(chisq_mntn_length_channel, context_col = "MntnLengthGroup") %>%
  group_by(MntnLengthGroup) %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()) 

chisq_mntn_length_channel_results
```

#### Robustness Check

```{r chisq-mention-length-channel-robust, results = 'asis'}
chisq_mntn_length_channel_robust <-  contingency_mntn_length_channel_time_robust %>%
  filter(ChannelTypeSplit != "NetworkNewsPre2000") %>%
  chisq.test(correct = FALSE)

chisq_mntn_length_channel_robust
```


**Total time spent discussing Supreme Court cases.**  
This was calculated on a robust sample, including only one instance of identical mentions.
```{r mention-length-total-channel-time}
#Total amount of time spent on SC cases by news sector
df_mntn_length_total_robust <- mntn_length_robust %>%
  group_by(ChannelTypeSplit) %>%
  summarise(MntnLengthTotal = sum(MntnLengthSeconds)) %>%
  mutate(MntnLengthTotal = lubridate::seconds_to_period(MntnLengthTotal)) %>%
  gt()

df_mntn_length_total_robust
```

### Cable News Program
This compares cable news mentions from the 2000-2018 terms.
```{r chisq-mention-length-cable, results='asis'}
#How long were Supreme Court case mentions on cable programs?
##Contingency table Channel Type ~ Story Length
contingency_mntn_length_cable <-  mntn_length %>%
  tabyl(NewsProgram, MntnLengthGroup) 

chisq_mntn_length_cable <- contingency_mntn_length_cable %>%
  filter(NewsProgram != "WorldNewsTonight") %>%
  chisq.test(correct = FALSE)

chisq_mntn_length_cable
```


```{r chisq-mention-length-cable-extra}
chisq_mntn_length_cable_results <- consolidate_chisq_results(chisq_mntn_length_cable, context_col = "MntnLengthGroup") %>%
  group_by(MntnLengthGroup) %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()) 

chisq_mntn_length_cable_results
```

#### Robustness Check
**Mention Length by Group**
```{r chisq-mention-length-cable-robust, results = 'asis'}
#How long were Supreme Court case mentions on cable programs?
##Contingency table Channel Type ~ Story Length
contingency_mntn_length_cable_robust <-  mntn_length_robust %>%
  tabyl(NewsProgram, MntnLengthGroup) 

chisq_mntn_length_cable_robust <- contingency_mntn_length_cable_robust %>%
  filter(NewsProgram != "WorldNewsTonight") %>%
  chisq.test(correct = FALSE)

chisq_mntn_length_cable_robust
```

**Total time spent discussing Supreme Court cases.**  
This was calculated on a robust sample, including only one instance of identical mentions.
```{r chisq-mention-length-total-cable-robust}
#Total amount of time spent on SC cases by news sector
MntnLengthTotal_cable <- mntn_length_robust %>%
  filter(ChannelTypeSplit == "CableNews") %>%
  group_by(NewsProgram) %>%
  summarise(MntnLengthTotal = sum(MntnLengthSeconds))  %>%
  mutate(MntnLengthTotal = lubridate::seconds_to_period(MntnLengthTotal)) %>%
  gt()

MntnLengthTotal_cable
```

```{r doodles, include = FALSE, eval = FALSE}
mntn_length %>%
  filter(ChannelTypeSplit == "NetworkNewsPost2000", MntnLengthGroup == "Short") %>%
  summary()

mntn_length %>%
  filter(ChannelTypeSplit == "NetworkNewsPost2000", MentionContext == 1) %>%
  summary()

#Quick visual to help me make sense of the data
mntn_length %>%
    pivot_longer(cols = AnchorOnly:NewsInterview,
               names_to = "SegmentFormat",
               values_to = "value") %>%
  filter(ChannelTypeSplit == "CableNews", value == 1) %>%
ggbarstats(x = SegmentFormat, y = MntnLengthGroup, type = "np", label = "counts")


mntn_length %>%
  filter(ChannelTypeSplit == "CableNews") %>%
ggbarstats(x = MentionContext, y = MntnLengthGroup, type = "np")

mntn_length %>%
  filter(ChannelTypeSplit == "NetworkNewsPost2000") %>%
ggbarstats(x = MentionContext, y = MntnLengthGroup, type = "np")

#Chisq for cable news mentions by length and mention context
contingency_cable_mntn_length_segment_topic <-  mntn_length %>%
  filter(ChannelTypeSplit == "CableNews") %>%
  tabyl(MntnLengthGroup, MentionContext) 

chisq_cable_mntn_length_segment_topic <- contingency_cable_mntn_length_segment_topic %>%
  chisq.test(correct = FALSE)

chisq_cable_mntn_length_segment_topic$expected
chisq_cable_mntn_length_segment_topic$stdres

mntn_length %>%
    pivot_longer(cols = AnchorOnly:NewsInterview,
               names_to = "SegmentFormat",
               values_to = "value") %>%
  filter(ChannelTypeSplit == "NetworkNewsPost2000", value == 1) %>%
ggbarstats(x = SegmentFormat, y = MntnLengthGroup, type = "np", label = "counts")

mntn_length %>%
  filter(ChannelTypeSplit == "NetworkNewsPost2000") %>%
  ggbarstats(x = MntnLengthGroup, y = MentionContext, type = "np", label = "both")

#mntn_length %>%
  #filter(ChannelTypeSplit == "CableNews") %>%
 # ggbetweenstats(x = MentionContext, y = MntnLengthSeconds, type = "np", xlab = "Thematic Context") +
 # scale_color_manual(values = pal_MentionContext)

ggsave("boxplot_length_context_cable.svg", width = 6.3, height = 4.72)


mntn_length %>%
    pivot_longer(cols = AnchorOnly:NewsInterview,
               names_to = "SegmentFormat",
               values_to = "value") %>%
  filter(ChannelTypeSplit == "CableNews", value == 1) %>%
grouped_ggbarstats(x = SegmentFormat, y = MntnLengthGroup, grouping.var = MentionContext, type = "np", label = "both")

#Cable Shows by Context and Format
#Create contingency table of segment format by mention context by news program
df_SegmentFormat_context_cable <- df_channel_split %>%
#Pivot df to long format
  pivot_longer(cols = AnchorOnly:NewsInterview,
               names_to = "SegmentFormat",
               values_to = "value") %>%
 #Reorder the segment format levels
  mutate(SegmentFormat = factor(SegmentFormat, levels = c("AnchorOnly", "Correspondent", "NewsInterview", "Debate"))) %>%
#Filter out World News from NewsProgram
  filter(NewsProgram != "WorldNewsTonight") %>%
#Drop World News from factor, otherwise it's in the table
  mutate(NewsProgram = fct_drop(NewsProgram))%>%
#Create table
  xtabs(value ~ NewsProgram + SegmentFormat + MentionContext, data = .)

#Convert xtabs to dataframe
df_SegmentFormat_context_cable <- as.data.frame(df_SegmentFormat_context_cable)

```