---
title: "NewsPresentationStats"
author: "Lisa Matthias"
date: "25 9 2023"
output: 
  html_document: 
    theme: readable
    toc: yes
    toc_float: yes
    code_folding: hide
---

```{r setup, echo=FALSE}
#set up global R to display 3 digits (0.000)
options
options(digits = 3)

#set up knit r global
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  fig.path = "figures/",
  fig.width = 6,
  fig.asp = 0.618,
  out.width = "70%",
  fig.align = "center",
  dpi = 300)
```

```{r packages, echo=FALSE}
library(datawizard)
library(gt)
library(janitor)
library(tidyverse)
```

```{r main-data, echo=FALSE}
# Read the local copy. Call this "mntn_emo"
mntn_emo <- read.csv("data/NewsEmotion.csv")
```

```{r variable-transformation, echo=FALSE}
# Set factor levels and labels
TimePeriodLevels <- c("2000_2018", "1990_1999")

# Mutate columns in mntn_emo
mntn_emo$ChannelType <- factor(mntn_emo$ChannelType,
  levels = c("NetworkNews", "CableNews")
)

mntn_emo$IssueArea <- factor(mntn_emo$IssueArea,
  levels = c("Abortion", "EconomicActivity", "FirstAmendment","Sex Discrimination"))

mntn_emo$NewsProgram <- factor(mntn_emo$NewsProgram, levels = c("Hardball", "SpecialReport", "WorldNewsTonight"))

mntn_emo$TimePeriod <- factor(mntn_emo$TimePeriod,
  levels = TimePeriodLevels
)

mntn_emo$MultiMentionType <- as.factor(mntn_emo$MultiMentionType)


mntn_emo <- mntn_emo %>%
  mutate(ChannelTypeSplit = case_when(ChannelType == "CableNews" &  TimePeriod == "2000_2018" ~ "CableNews", ChannelType == "NetworkNews" &  TimePeriod == "2000_2018" ~ "NetworkNewsPost2000", ChannelType == "NetworkNews" &  TimePeriod == "1990_1999" ~ "NetworkNewsPre2000"))

mntn_emo$ChannelTypeSplit <- factor(mntn_emo$ChannelTypeSplit, levels = c("NetworkNewsPre2000", "NetworkNewsPost2000", "CableNews"))

#Robustness set with Identical news mentions included only once
# Create a new dataframe that only includes entries with "MultiMentionMentionType" == "Identical"
mntn_emo_Identical <- mntn_emo[mntn_emo$MultiMentionType == "Identical",]

# Use the unique function to only keep the first instance of each "TranscriptID" for Identicals
mntn_emo_Identical <- mntn_emo_Identical[!duplicated(mntn_emo_Identical$TranscriptID),]

# Create a new dataframe that only includes entries with "MultiMentionMentionType" != "Identical"
mntn_emo_non_Identical <- mntn_emo[mntn_emo$MultiMentionType != "Identical",]

# Concatenate the filtered dataframes
mntn_emo_robust <- rbind(mntn_emo_non_Identical, mntn_emo_Identical)

```


```{r chisq-functions, echo=FALSE}
#Function for chisq pre-2000 & post-2000 network news
function_chisq_emo_pre2000 <- function(df, news_var, var){
  news_var <- sym(news_var)
  var <- sym(var)
  
  x <- df %>%
  filter(ChannelTypeSplit != "CableNews") %>%
  mutate_if(is.numeric,as.factor) %>%
  tabyl(!!news_var , !! var, show_missing_levels = FALSE) %>%
  chisq.test(correct = FALSE)
  
  return(x)
}

#Function for chisq post-2000 network & cable news 
function_chisq_emo_post2000 <- function(df, news_var, var){
  news_var <- sym(news_var)
  var <- sym(var)
  
  x <- df %>%
  filter(ChannelTypeSplit != "NetworkNewsPre2000") %>%
  mutate_if(is.numeric,as.factor) %>%
  tabyl(!!news_var , !! var, show_missing_levels = FALSE) %>%
  chisq.test(correct = FALSE)
  
  return(x)
}

#Function for chisq cable programs
function_chisq_emo_cable <- function(df, news_var, var){
  news_var <- sym(news_var)
  var <- sym(var)
  
  x <- df %>%
  filter(ChannelTypeSplit == "CableNews") %>%
  mutate_if(is.numeric,as.factor) %>%
  tabyl(!!news_var , !! var, show_missing_levels = FALSE) %>%
  chisq.test(correct = FALSE)
  
  return(x)
}

#Function to print chisq results, observed values, expected values, and standardized residuals
consolidate_chisq_results <- function(chisq_context_time, context_col) {
  
  observed <- chisq_context_time$observed
  expected <- chisq_context_time$expected
  stdres <- chisq_context_time$stdres
  
  # Dynamically get the name of the first column
  first_col_name <- colnames(observed)[1]
  
    result_df <- data.frame(
      FirstColumn = observed[, 1],
      Observed_1 = observed[, 2],
      Observed_2 = observed[, 3],
      Expected_1 = expected[, 2],
      Expected_2 = expected[, 3],
      StdRes_1 = stdres[, 2],
      StdRes_2 = stdres[, 3]
    )
  
  long_df <- result_df %>%
    pivot_longer(
      cols = starts_with("Observed") | starts_with("Expected") | starts_with("StdRes"),
      names_to = c(".value", context_col),
      names_pattern = "(Observed|Expected|StdRes)_(\\d+)"
    ) %>%
    select(FirstColumn, all_of(context_col), Observed, Expected, StdRes) %>%
    rename_at(vars(FirstColumn), ~first_col_name)  # Rename 'FirstColumn' back to its original name
  
 long_df <- long_df %>%
    mutate(
      !!context_col := case_when(
        context_col == "Present" ~ factor(!!sym(context_col), levels = c("1", "2"), labels = c("No", "Yes")),
        context_col == "EmotionType" ~ factor(!!sym(context_col), levels = c("1", "2"), labels = c("NegativeEmotion", "PositiveEmotion")),
        TRUE ~ as.factor(!!sym(context_col))
      ),
      Expected = round(Expected, digits = 2),
      StdRes = round(StdRes, digits = 2)
    )
  
  return(long_df)
}
```

## Presence of Emotional Appeals

This compares robust samples of news mentions between channel types and time periods and checks whether the share of news mentions with emotional appeals present/absent is comparable between them.

### Network News Time Periods

This compares network news mentions from the 1990-1999 and 2000-2018 terms.

```{r chisq-emo-present-time-period-robust, results='asis'}
#Robust with identical mentions left out
#Chi-Squared for pre-2000 and post-2000 network news ~ emotion
chisq_emo_time_robust <- function_chisq_emo_pre2000(mntn_emo_robust, news_var = "ChannelTypeSplit", var = "EmotionPresent")

chisq_emo_time_robust
```

### Channel Type

This compares network and cable news mentions from the 2000-2018 terms.

```{r chisq-emo-present-channel-robust, results='asis'}
#Chi-Squared for post-2000 network news and cable news ~ emotion
chisq_emo_channel_robust <- function_chisq_emo_post2000(mntn_emo_robust, news_var = "ChannelTypeSplit", var = "EmotionPresent")

chisq_emo_channel_robust

```


### Cable News Program

This compares Hardball (MSNBC) and  Special Report (Fox News) news mentions from the 2000-2018 terms.

```{r chisq-emo-present-cabel-robust, results='asis'}
#Chi-Squared for Hardball and Special Report ~ emotion
chisq_emo_cable_robust <- function_chisq_emo_cable(mntn_emo_robust, news_var = "NewsProgram", var = "EmotionPresent")

chisq_emo_cable_robust
```

```{r chisq-emo-present-cabel-robust-extra}
chisq_emo_cable_robust_results <- consolidate_chisq_results(chisq_emo_cable_robust, context_col = "Present") %>%
  group_by(Present) %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups())

chisq_emo_cable_robust_results
```

### Not Robust
This is just to show the results with the full sample.

**First the network news time periods.**

```{r chisq-emo-present-time-period-unfiltered, , results='asis'}
#Chi-Squared for pre-2000 and post-2000 network news ~ emotion
chisq_emo_time_unfiltered <- function_chisq_emo_pre2000(mntn_emo, news_var = "ChannelTypeSplit", var = "EmotionPresent")

chisq_emo_time_unfiltered
```

**Then network and cable news, 2000-2018 terms.**

```{r chisq-emo-present-channel-unfiltered, results='asis'}
#Chi-Squared for post-2000 network news and cable news ~ emotion
chisq_emo_channel_unfiltered <- function_chisq_emo_post2000(mntn_emo, news_var = "ChannelTypeSplit", var = "EmotionPresent")

chisq_emo_channel_unfiltered
```

**And the cable programs.**

```{r chisq-emo-present-cable-unfiltered, results='asis'}
#Chi-Squared for Hardball and Special Report ~ emotion
chisq_emo_cable_unfiltered <- function_chisq_emo_cable(mntn_emo, news_var = "NewsProgram", var = "EmotionPresent")

chisq_emo_cable_unfiltered
```


## Type of Emotional Appeals

This compares news samples based on the share of positive/negative emotional appeals included in the news mentions as well as the distinct emotions featured most frequently.

### Network News Time Period
This compares network news mentions from the 1990-1999 and 2000-2018 terms.

```{r rchisq-emo-type-time-period-robust, results='asis'}
contingency_emo_type_channels_robust <- mntn_emo_robust %>%
  filter(EmotionPresent == "1") %>%
  group_by(ChannelTypeSplit) %>%
  summarise(NegativeEmotion = sum(NegativeEmotion, na.rm = TRUE),
            PositiveEmotion = sum(PositiveEmotion, na.rm = TRUE)) %>%
  as_tabyl()

chisq_emo_type_time_robust <- contingency_emo_type_channels_robust %>%
  filter(ChannelTypeSplit != "CableNews") %>%
  janitor::chisq.test(correct = FALSE)

chisq_emo_type_time_robust
```

### Channel Type
This compares network and cable news mentions from the 2000-2018 terms.

```{r chisq-emo-type-channel-robust, results='asis'}
chisq_emo_type_channel_robust <- contingency_emo_type_channels_robust %>%
  filter(ChannelTypeSplit != "NetworkNewsPre2000") %>%
  janitor::chisq.test(correct = FALSE)

chisq_emo_type_channel_robust
```


### Cable News Programs

This compares Hardball (MSNBC) and  Special Report (Fox News) news mentions from the 2000-2018 terms.

```{r chisq-emo-type-cable-robust, results='asis'}
contingency_emo_type_cable_robust <- mntn_emo_robust %>%
  filter(EmotionPresent == "1") %>%
  group_by(NewsProgram) %>%
  summarise(NegativeEmotion = sum(NegativeEmotion, na.rm = TRUE),
            PositiveEmotion = sum(PositiveEmotion, na.rm = TRUE)) %>%
  as_tabyl()

chisq_emo_type_cable_robust <- contingency_emo_type_cable_robust %>%
  filter(NewsProgram != "WorldNewsTonight") %>%
  janitor::chisq.test(correct = FALSE)
  
chisq_emo_type_cable_robust
```

```{r chisq-emo-type-cable-robust-extra}
chisq_emo_type_cable_robust_results <- consolidate_chisq_results(chisq_emo_type_cable_robust, context_col = "EmotionType") %>%
  group_by(EmotionType) %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()) %>%
  tab_footnote(
  footnote = "A = Hardball; B = Special Report"
)

chisq_emo_type_cable_robust_results
```

```{r results-channel-emo-type-median-robust, include=FALSE}
### When Emotional Appeals Were Included, How Many On Avg?

#Getting the mean and median number of positive and negative emotional appeals per news sample.


#Get median and mean
median_channel <- mntn_emo_robust %>%
  filter(EmotionPresent == "1") %>%
  group_by(ChannelTypeSplit)  %>%
  summarize(mean_value_pos = mean(PositiveEmotion, na.rm = TRUE),
            median_value_pos = median(PositiveEmotion, na.rm = TRUE),
            mean_value_neg = mean(NegativeEmotion, na.rm = TRUE),
            median_value_neg = median(NegativeEmotion, na.rm = TRUE))

median_channel
```


```{r results-cable-emo-type-median-robust, include=FALSE}
#Get median and mean
median_cable <- mntn_emo_robust %>%
  filter(EmotionPresent == "1") %>%
  group_by(NewsProgram)  %>%
  summarize(mean_value_pos = mean(PositiveEmotion, na.rm = TRUE),
            median_value_pos = median(PositiveEmotion, na.rm = TRUE),
            mean_value_neg = mean(NegativeEmotion, na.rm = TRUE),
            median_value_neg = median(NegativeEmotion, na.rm = TRUE))

median_cable
```


```{r results-time-period-emo-unfiltered, include=FALSE}
### Not Robust 
contingency_emo_type_channels <- mntn_emo %>%
  filter(EmotionPresent == "1") %>%
  group_by(ChannelTypeSplit) %>%
  summarise(NegativeEmotion = sum(NegativeEmotion, na.rm = TRUE),
            PositiveEmotion = sum(PositiveEmotion, na.rm = TRUE)) %>%
  as_tabyl()

chisq_emo_type_channels <- contingency_emo_type_channels %>%
  filter(ChannelTypeSplit != "CableNews") %>%
  janitor::chisq.test(correct = FALSE) 
```


```{r results-channel-emo-unfiltered, include=FALSE}
# Cable and network news.
chisq_emo_type_post2000 <- contingency_emo_type_channels %>%
  filter(ChannelTypeSplit != "NetworkNewsPre2000") %>%
  janitor::chisq.test(correct = FALSE)
```

## Most Frequently Used Emotions

### Channel Type and Time Period, Top 3.

```{r top3-emo-channel-time-robust}
top3_emo_channel <- mntn_emo_robust %>%
  select(ChannelTypeSplit, NegativeEmotionAlarming:PositiveEmotionThing) %>%
  group_by(ChannelTypeSplit) %>%
summarise(across(everything(), list(sum))) %>%
  group_by(ChannelTypeSplit) %>%
  pivot_longer(cols = NegativeEmotionAlarming_1:PositiveEmotionThing_1,
               names_to = "EmotionTypeSpec",
               values_to = "n") %>%
  arrange(desc(n)) %>% 
  slice(1:3)

top3_emo_channel_results <- top3_emo_channel %>%
  group_by(ChannelTypeSplit) %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()) 

top3_emo_channel_results

```

```{r results-news-channel-top5-emo, include=FALSE}
top5_emo_channel <- mntn_emo_robust %>%
  select(ChannelTypeSplit, NegativeEmotionAlarming:PositiveEmotionThing) %>%
  group_by(ChannelTypeSplit) %>%
summarise(across(everything(), list(sum))) %>%
  group_by(ChannelTypeSplit) %>%
  pivot_longer(cols = NegativeEmotionAlarming_1:PositiveEmotionThing_1,
               names_to = "EmotionTypeSpec",
               values_to = "n") %>%
  arrange(desc(n)) %>% 
  slice(1:5)
```

### Cable News Program, Top 3.

```{r results-news-cable-top3-emo}
top3_emo_cable <- mntn_emo_robust %>%
  filter(ChannelTypeSplit == "CableNews") %>%
  select(NewsProgram, NegativeEmotionAlarming:PositiveEmotionThing) %>%
  group_by(NewsProgram) %>%
summarise(across(everything(), list(sum))) %>%
  group_by(NewsProgram) %>%
  pivot_longer(cols = NegativeEmotionAlarming_1:PositiveEmotionThing_1,
               names_to = "EmotionTypeSpec",
               values_to = "n") %>%
  arrange(desc(n)) %>% 
  slice(1:3)

top3_emo_cable_results <- top3_emo_cable %>%
  group_by(NewsProgram) %>%
  gt() %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()) 

top3_emo_cable_results
```


```{r results-channel-type-quotes-para, include=FALSE, eval=FALSE}
## Snippets for writing
#Create filter, so that "Cert" "PostCert", and "PostArgument" are removed from df, and only remaining case stages are included
cert_arg_removed <- c("PostDecision", "Decision", "Argument")

#Create table with quote and paraphrase counts by case stage and channel type
qt_para_channel <- mntn_emo_robust %>%
  filter(CaseStage %in% cert_arg_removed) %>%
  select(ChannelTypeSplit, CaseStage, MajQt:ArgPara) %>%
  group_by(ChannelTypeSplit, CaseStage) %>%
summarise(across(everything(), list(sum))) 

#Create table with quote and paraphrase counts by case stage and news sector
qt_para_channel_main <- mntn_emo_robust %>%
  filter(CaseStage %in% cert_arg_removed) %>%
  select(ChannelTypeSplit, CaseStage, MajQt:ArgPara) %>%
  group_by(ChannelTypeSplit, CaseStage) %>%
summarise(across(everything(), list(sum))) 
```


```{r info-snippets-for-writing, include=FALSE, eval=FALSE}
#Calculate how many news mentions and emotional appeals are in the main sample and the robust sample
appeals_n <- mntn_emo %>% 
  summarise(n_mntns_total = n(),
            n_emo = sum(NegativeEmotion + PositiveEmotion))

appeals_n_robust <- mntn_emo_robust %>% 
  summarise(n_mntns_total = n(),
            n_emo = sum(NegativeEmotion + PositiveEmotion))


#Get number of news mentions that include at least 1 direct quote: Channel Type
mntns_qt_stage_count_channel <-  mntn_emo_robust %>%
  filter(CaseStage == "Decision" | CaseStage == "Argument") %>%
  group_by(ChannelTypeSplit, CaseStage) %>%
  summarise(n_mntns_total = n(),
            n_mntns_qt = sum(
              (CaseStage == "Decision" & (MajQt > 0 | DissQt > 0)) | 
                (CaseStage == "Argument" & ArgQt > 0)),
            n_arg_qt = sum(ArgQt),
            n_maj_qt = sum(MajQt),
            n_diss_qt = sum(DissQt))

#Get number of news mentions that include at least 1 direct quote: Cable News
mntns_qt_stage_count_cable <-  mntn_emo_robust %>%
  filter(ChannelTypeSplit == "CableNews") %>%
  filter(CaseStage == "Decision" | CaseStage == "Argument") %>%
  group_by(NewsProgram, CaseStage) %>%
  summarise(n_mntns_total = n(),
            n_mntns_qt = sum(
              (CaseStage == "Decision" & (MajQt > 0 | DissQt > 0)) | 
                (CaseStage == "Argument" & ArgQt > 0)),
            n_arg_qt = sum(ArgQt),
            n_maj_qt = sum(MajQt),
            n_diss_qt = sum(DissQt))


num_rows <-  mntn_emo_robust %>%
  filter(NewsProgram == "SpecialReport") %>%
  filter(MajQt == 0, MajPara == 0, DissQt == 0, DissPara == 0, ArgQt == 0, ArgPara == 0) %>%
  nrow()

#Find out how many emotions are present by News Program
# Group the dataframe by "NewsProgram"
distinct_emo_count_df <-  mntn_emo_robust %>% 
  group_by(NewsProgram)

  # Sum the columns from NegativeEmotionAlarming to PositiveEmotionThing for each group
  distinct_emo_count <- distinct_emo_count_df %>% summarise(across(NegativeEmotionAlarming:PositiveEmotionThing, sum)) %>%
     pivot_longer(cols = NegativeEmotionAlarming:PositiveEmotionThing, names_to = "Emo", values_to = "n") %>%
     filter(n > 0) %>%
      group_by(NewsProgram) %>%
  summarise(num_rows = n())
  
  
  #Find out how many emotions are present by ChannelTypeSplit
# Group the dataframe by "ChannelTypeSplit"
distinct_emo_count_df <-  mntn_emo_robust %>% 
  group_by(ChannelTypeSplit)

  # Sum the columns from NegativeEmotionAlarming to PositiveEmotionThing for each group
  distinct_emo_count <- distinct_emo_count_df %>% summarise(across(NegativeEmotionAlarming:PositiveEmotionThing, sum)) %>%
     pivot_longer(cols = NegativeEmotionAlarming:PositiveEmotionThing, names_to = "Emo", values_to = "n") %>%
     filter(n > 0) %>%
      group_by(ChannelTypeSplit) %>%
  summarise(num_rows = n())
  

 neg_general_plus_fear_channel_type <- mntn_emo_robust %>%
    group_by(ChannelTypeSplit) %>%
    summarise(Neg = sum(NegativeEmotionDimensionGeneral+NegativeEmotionFear))
 

##Doodles
  mntn_emo_robust$CaseStageCondensed <- fct_collapse(mntn_emo_robust$CaseStage,
  "PreDecision" = c(
    "Cert", "PostCert",
    "Argument", "PostArgument"),
  "Decision" = "Decision",
  "PostDecision" = "PostDecision"
)

mntn_emo_robust$CaseStageCondensed <- factor(mntn_emo_robust$CaseStageCondensed, levels = c("PreDecision", "Decision", "PostDecision"), labels = c("PreDecision", "Decision", "PostDecision"))

##include this in github repo (past-Lisa didn't leave a note why to include this)
violin_channel_neg_case_stage <-
mntn_emo_robust %>%
  filter(ChannelTypeSplit != "NetworkNewsPre2000") %>%
ggstatsplot::grouped_ggbetweenstats(x = CaseStageCondensed, y = NegativeEmotion, grouping.var = ChannelTypeSplit, type = "np")

violin_channel_neg_case_stage
```
  